\entry{Level}{
	When playing a video game, every object 
	that you see or interact with resides in 
	what is known as a Level. In Unreal Engine 4 terms, 
	a Level is made up of a collection of Static Meshes \ref{Mesh}, 
	Volumes \ref{Volume}, Lights \ref{Light}, Blueprints \ref{Blueprint} 
	and more all working together 
	to bring the desired experience to the player. 
	Levels in UE4 can range in size from massive 
	terrain-based worlds to very small levels 
	that contain a few Actors \ref{Actor}.

	A Level is a user defined area of gameplay. 
	Levels are created, viewed, and modified 
	mainly by placing, transforming, and editing 
	the properties of the Actors \ref{Actor} it 
	contains. In the Unreal Editor, 
	each Level is saved as a separate \texttt{.umap} 
	file, which is also why you will 
	sometimes see them referred to as Maps.
}

\entry{Light}{
	Unreal Engine 4 has four light types: 
	\begin{itemize}
		\item Directional \ref{Directional Light}
		\item Point \ref{Point light}
		\item Spot \ref{Spot light}
		\item Sky \ref{Sky light}
		\item Rect \ref{Rect light}
	\end{itemize}
	Directional lights are primarily used as your primary outdoor 
	light or any light that needs to appear as if it is 
	casting light from extreme or near-infinite distances. 
	Point lights are your classic "light bulb" like light, 
	emitting light in all directions from a single point. 
	Spot lights emit light from a single point, but have their
	 light limited by a set of cones. Sky lights capture the
	  background of your scene and apply it as lighting to 
	  your level's meshes.
}

\entry{Lighting Pass}{
	Emphasis is placed on improving lighting \ref{Light}, 
	adding PostProcess effects and updating materials \ref{Material}.
}